### 2021-10-30 README.Rmd
Added dependency on ggplot2 instead of using as an import

[`ggplot2`](https://ggplot2.tidyverse.org/) requires wide format data to be 
wrangled into long format for plotting, which can be quite cumbersome when 
creating simple plots. Therefore, the motivation for `ggmatplot` was to provide 
a solution that allows [`ggplot2`](https://ggplot2.tidyverse.org/) to handle 
wide format data. Although `ggmatplot` doesn't provide the same flexibility 
as [`ggplot2`](https://ggplot2.tidyverse.org/), it can be used as a 
workaround for having to wrangle wide format data into long format for plotting 
with [`ggplot2`](https://ggplot2.tidyverse.org/).

@@

```{r}
library(ggmatplot)
library(ggplot2)
```

>>>>

[`ggplot2`](https://ggplot2.tidyverse.org/) requires wide format data to be 
wrangled into long format for plotting, which can be quite cumbersome when 
creating simple plots. Therefore, the motivation for `ggmatplot` was to provide 
a solution that allows [`ggplot2`](https://ggplot2.tidyverse.org/) to handle 
wide format data. Although `ggmatplot` doesn't provide the same flexibility 
as [`ggplot2`](https://ggplot2.tidyverse.org/), it can be used as a 
workaround for having to wrangle wide format data into long format and creating
simple plots using [`ggplot2`](https://ggplot2.tidyverse.org/).

@@

```{r}
library(ggmatplot)
```
